NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-01-22 Manuscript/manuscriptPS.tex
Update authorlist
Add data by J. Madsen

\author{Pavel Buslaev}
\affiliation{Moscow Institute of Physics and Technology}
\author{Tiago M. Ferreira}
\affiliation{Halle, Germany}
\author{Ivan Gushchin}
\affiliation{Moscow Institute of Physics and Technology}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Batuhan Kav}
\affiliation{Potsdam, Germany}
\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois 60637, United States of America}
\author{Markus Miettinen}
\affiliation{Potsdam, Germany}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Ricky Nencini}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{O. H. Samuli Ollila}
\email[]{samuli.ollila@helsinki.fi}
%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
\author{Thomas Piggot   \todo{Authorlist is not yet complete}}
\affiliation{Southampton, United Kingdom}
%\author{NMRlipids collaboration}
%\affiliation{nmrlipids.blogspot.fi}

@@

    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 0.26 & 250:50 & 11190  & 53  & 298  & 200 & ? \todoi{Equilibration time to be checked}  & \cite{POPC5POPS1withCaClCHARMM}   \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 1 \todoi{Concentration to be checked after the amount of water molecules is known.} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\

>>>>

\author{Pavel Buslaev}
\affiliation{Moscow Institute of Physics and Technology}
\author{Fernando Favela}
\affiliation{Mexico}
\author{Tiago M. Ferreira}
\affiliation{Halle, Germany}
\author{Ivan Gushchin}
\affiliation{Moscow Institute of Physics and Technology}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Batuhan Kav}
\affiliation{Potsdam, Germany}
\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois 60637, United States of America}
\author{Markus Miettinen}
\affiliation{Potsdam, Germany}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{Ricky Nencini}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\author{O. H. Samuli Ollila}
\email[]{samuli.ollila@helsinki.fi}
%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
\author{Thomas Piggot   \todo{Authorlist is not yet complete}}
\affiliation{Southampton, United Kingdom}
%\author{NMRlipids collaboration}
%\affiliation{nmrlipids.blogspot.fi}

@@

    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 0.26 & 250:50 & 11190  & 53  & 298  & 200 & 180 & \cite{POPC5POPS1withCaClCHARMM}   \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 1.06 & 250:50 & 11174  & 214  & 298  & 200 & ?  & \cite{POPC5POPS1with1MCaClCHARMM}  \\
